---
title: "Sliced S1_e11 Semi Final - my attempt"
output: html_notebook
---

# having a look at texas house prices
    I think I will try focus on viz with a bit of numerical ML modelling, text might be a bit too tricky for me

```{r}
library(tidyverse)
library(tidymodels)
library(janitor)

```

# column information
    uid - the unqiue house ID
    city - all austin/texas except 1 house
    description - description listing of house (Appears to contain the zipcode which we could try to extract as it appears to be after "TX ")
    homeType - 10 different options, ranging from SIngle Family, town house, vacant land, multiFamily, mobile, condo etc.
    latitude
    longitude
    garageSpaces - number of car slots in garage, from 0 - 22!!
    hasSpa - does it have a spa?
    yearBuilt - 
    numberOfPatioAndPorchFeatures -
    lotSizeSqFt - lot size, goes from very small (100 sqft) to massive, 34154525!!
    avgSchoolRating - 2.33 to 9.5 (Im guessing scale of 1 to 10) average rating of all school types nearby
    MedianStudentsPerTeacher - ranges from 10 to 19 
    numOfBathrooms 
    numOfBedrooms
    priceRange
    

```{r}
train <- read_csv('C:/Users/hgre955/Downloads/sliced_s1_e11_train.csv')
test <- read_csv('C:/Users/hgre955/Downloads/sliced_s1_e11_test.csv')
example_sub <- read_csv('C:/Users/hgre955/Downloads/sliced_s1_e11_sample.csv')




```
#exploring the data set

```{r}
train %>% filter(lotSizeSqFt > 500000)


```

# prepare the data for modelling

```{r}

# The sample submission categorizes this into price brackets from 0-250000, 250000 - 350000, 350000 - 450000,450000 - 650000, 650000 +
# what sort of model can be used to give probablilites of categorising 


```

